---
title: "hw5"
author: "Yan Li"
date: "2024-11-13"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


# Problem 1
## Birthday Function
```{r}
bday_dupes = function(n) {
  bdays = sample(1:365, size = n, replace = TRUE)
  has_dupe = any(duplicated(bdays))
  return(has_dupe)
}

```
## Run function for different group size
```{r}
set.seed(123)
results = map_df(2:50, function(n) {
  dupes = map_lgl(1:10000, ~ bday_dupes(n))
  prob = mean(dupes)
  tibble(group_size = n, prob = prob)
})
```
## Plot
```{r}
ggplot(results, aes(x = group_size, y = prob)) +
  geom_line() +
  labs(
    title = "Problem 1:Birthday Function",
    x = "Group Size",
    y = "Probability of Shared Birthday"
  )
```
- The probability of shared birthday increases as the group size increases, and the growth in probability is nonlinear.

# Problem 2
## t-test

```{r}
set.seed(123)
n = 30
sigma = 5
mu_values = c(0, 1, 2, 3, 4, 5, 6)
num_sim = 5000

run_sim = function(mu) {
  replicate(num_sim, {
    x = rnorm(n, mean = mu, sd = sigma)
    t_test = t.test(x, mu = 0)
    broom::tidy(t_test)
  }, simplify = FALSE) |>
    bind_rows() |>
    mutate(mu = mu)
}

simulations = map_df(mu_values, run_sim)
```

## Power and Estimate Mu
```{r}
results_df = simulations |>
  group_by(mu) |>
  summarize(
    power = mean(p.value < 0.05),
    avg_mu_est = mean(estimate),
    avg_rej_mu_est = mean(estimate[p.value < 0.05], na.rm = TRUE)
  )

results_df
```
##  Plot 1: Power vs True mu
```{r}

results_df |>
  ggplot(aes(x = mu, y = power)) +
  geom_line() +
  labs(
    title = "Power vs True mu",
    x = "True mu",
    y = "Power (Proportion of Null Rejections)"
  )
```
- The relationship between effect size and power is positive. As the effect size increases, power also increases,

## Plot 2: Average estimate mu vs True mu
```{r}

results_df |>
  ggplot(aes(x = mu)) +
  geom_line(aes(y = avg_mu_est), color = "blue") +
  geom_line(aes(y = avg_rej_mu_est), color = "red") +
  labs(
    title = "Average Estimate mu vs True mu",
    x = "True mu",
    y = "Average Estimate"
  )

```
- No, the sample average of estimate mu across tests for which the null is rejected is not approximately equal to the true value of mu.The average estimate mu is consistently higher than the true value of mu for the cases where the null hypothesis was rejected.Because more samples reject the null, including those closer to the true value, will lead to a reduction in bias.So the red line becomes closer to the blue line as mu increases. 

# Problem 3
## Import Data
```{r}
homicide = read_csv("./homicide-data.csv")
```
- This dataset has 52179 observations and 12 variables, it provides a detailed look at homicide incidents across various U.S. cities, including victim information (name, race, age, sex), location data (latitude, longitude, city, state), and the current status of the case.

## Create new variable
```{r}
homicide_new = homicide |>
  mutate(city_state = paste(city, state, sep = ", "))

```
##  Total homicides and unsolved homicides
```{r}
total_homi = homicide_new |>
  group_by(city_state) |>
  summarize(
    total_homicides = n(),
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  )

total_homi
```

## Proportion of Homicides in Baltimore
```{r}
baltimore = total_homi |>
  filter(city_state == "Baltimore, MD") |>
  summarise(
    prop_test = prop.test(unsolved_homicides, total_homicides) |> broom::tidy()
  ) |>
  unnest(prop_test) |>
  select(estimate, conf.low, conf.high) 

baltimore

```
- In Baltimore, MD, an estimated 64.6% of homicides remain unsolved, with a 95% confidence interval ranging from 62.8% to 66.3%. 

## Proportion for Each City
```{r}
city_porp = total_homi |>
  mutate(
    prop_result = purrr::map2(unsolved_homicides, total_homicides, ~ prop.test(x = .x, n = .y))
  ) |>
  mutate(
    prop_result = purrr::map(prop_result, broom::tidy)
  ) |>
  unnest(prop_result) |>
  select(city_state, estimate, conf.low, conf.high)
  
city_porp
```

## PLOT
```{r}
ggplot(city_porp, aes(x = reorder(city_state, estimate), y = estimate, color = city_state)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.3) +
  coord_flip() +
  labs(
    title = "Proportion of Unsolved Homicides by City",
    x = "City",
    y = "Proportion of Unsolved Homicides"
  ) +
  theme(legend.position = "none")
```





