---
title: "hw5"
author: "Yan Li"
date: "2024-11-13"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(ggplot2)
library(readxl)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


# Problem 1
## Birthday Function
```{r}
bday_dupes = function(n) {

  bdays = sample(1:365, size = n, replace = TRUE)
  
  has_dupe = any(duplicated(bdays))
  
  return(has_dupe)
}

```
## Run function for different group size
```{r}
set.seed(123)
results = map_df(2:50, function(n) {
  dupes = map_lgl(1:10000, ~ bday_dupes(n))
  prob = mean(dupes)
  tibble(group_size = n, prob = prob)
})
```
## Plot
```{r}
ggplot(results, aes(x = group_size, y = prob)) +
  geom_line() +
  labs(
    title = "Problem 1:Birthday Function",
    x = "Group Size",
    y = "Probability of Shared Birthday"
  )
```
- The probability of shared birthday increases as the group size increases, and the growth in probability is nonlinear.

# Problem 2
## t-test
```{r}
set.seed(123)
n = 30
sigma = 5
mu_vals = 0:6

p_values = function(mu) {
  map_dbl(1:5000, ~ {
    x = rnorm(n, mean = mu, sd = sigma)
    t_test = t.test(x, mu = 0)
    broom::tidy(t_test)$p.value
  })
}

power_results = map_df(mu_vals, function(mu) {
  p_vals = p_values(mu)
  power = mean(p_vals < 0.05)
  return(tibble(mu = mu, power = power))
})

power_results
```
## Plot Power
```{r}
ggplot(power_results, aes(x = mu, y = power)) +
  geom_line() +
  labs(
    title = "Power of T-Test",
    x = "True Value of Mu",
    y = "Power"
  )
```
- The plot shows a positive relationship between effect size (mu) and statistical power. As the effect size (mu) increases, the power of the test also increases. 

## Plot True mu
```{r}
mu_hat = function(mu) {
  map_dbl(1:5000, ~ {
    x = rnorm(n, mean = mu, sd = sigma)
    mean(x)
  })
}

mu_hat2 = map_df(mu_vals, function(mu) {
  mu_hats = mu_hat(mu)
  avg_mu_hat = mean(mu_hats)
  return(tibble(mu = mu, avg_mu_hat = avg_mu_hat))
})

ggplot(mu_hat2, aes(x = mu, y = avg_mu_hat)) +
  geom_line() +
  labs(
    title = "Average Mu_hat vs True Mu",
    x = "True Value of Mu",
    y = "Average Estimate of Mu_hat"
  )
```



